k-plus Anticlustering: An Improved k-means Criterion for Maximizing Between-Group Similarity

### 2023-05-04 paper.Rmd
this is consistent with the other ones

Note that there is a direct connection between the $\mathit{SSE}$ and the location of the cluster centroids [@spath1986]. If the $\mathit{SSE}$ is minimal---which is the goal of k-means *clustering*---, the centroid values $\overline{\mathbf{x}}^{(k)} (k = 1, \ldots, K)$ are as far away as possible from the overall data centroid $\overline{\mathbf{x}} = (\overline{\mathbf{x}}_1, \overline{\mathbf{x}}_2, \ldots, \overline{\mathbf{x}}_P$), where $\overline{\mathbf{x}}_j$ ($j = 1, \ldots, P$) is the overall mean value on the $j$th attribute:

>>>>

Note that there is a direct connection between the $\mathit{SSE}$ and the location of the cluster centroids [@spath1986]. If the $\mathit{SSE}$ is minimal---which is the goal of k-means *clustering*---, the centroid values $\overline{\mathbf{x}}^{(k)} (k = 1, \ldots, K)$ are as far away as possible from the overall data centroid $\overline{\mathbf{x}} = (\overline{\mathbf{x}}_1, \overline{\mathbf{x}}_2, \ldots, \overline{\mathbf{x}}_P$), where $\overline{\mathbf{x}}_j$ ($j = 1, \ldots, P$) is the overall mean value on the $j$'th attribute:
